Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-15 doc/manuscript/ESSDmanuscript.tex
litter section

The International Panel on Climate Change (IPCC) provides guidance for
national greenhouse gas inventories for reporting to the United Nations
Framework Convention on Climate Change
\citep[UNFCCC,][]{ipcc_2006_2006, ipcc_2019_2019}. Under this guidance,
greenhouse gas inventories include all managed land, including most of
the world's forest land \citep{ogle_delineating_2018}. The IPCC
inventory guidelines include specific instructions for accounting for
greenhouse gas (mainly CO\textsubscript{2}) exchanges between forest
land and the atmosphere \citep{ipcc_agriculture_2006, ipcc_2019_2019}.
This guidance has improved over the years as more of the relevant
underlying data has become available
\citep{requenasuarez_estimating_2019, rozendaal_aboveground_2022}, but
there remains room for continuous improvement as the science advances.
For example, the year following the release of the latest IPCC
guidelines, \citet{cook-patton_mapping_2020} found that the latest
default rates may underestimate rates of C accumulation in regrowth
forests by 32\% on average and fail to capture eight-fold variation
within ecozones. In addition, \citet{cuni-sanchez_high_2021} found that
aboveground C stocks in mature African tropical montane forests were
two-thirds higher than the IPCC default values for these forests. This
rapid evolution of scientific information on the climate mitigation
potential of forests is beneficial to climate mitigation efforts, but
requires improved mechanisms for communicating the latest information
from scientific researchers to the practitioners who need reliable
estimates for greenhouse gas mitigation planning. Moreover, high
variability of forest C cycling within ecozones
\citep[e.g.,][]{cook-patton_mapping_2020, cuni-sanchez_high_202} implies
that it is useful for practitioners to have access to locally-specific
information, when available.

@@

\caption{\label{tab:table_pools}\textbf{IPCC-defined forest carbon pools with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{pool} & \textbf{definition} & \textbf{important sources of estimate variation} & \textbf{IPCC guidance}\\
\hline
aboveground biomass & all biomass of living vegetation & min dbh & may exclude understory if minor component\\
\hline
 &  & include non-dicot trees? & ?\\
\hline
 &  & include dead standing? & no\\
\hline
 &  & biomass allometry & ?\\
\hline
belowground biomass & all biomass of live roots & all factors relevant to aboveground biomass & see above\\
\hline
 &  & allometry or assumed ratio of below- to above-ground biomass (R) & can estimate based on R\\
\hline
 &  & min root diameter & may exclude fine roots\\
\hline
 &  & sampling depth & ?\\
\hline
dead wood & all non-living woody biomass above a specified diameter, aboveground or belowground & min diameter & 10 cm default, but may be chosen by country\\
\hline
 &  & include belowground? & \vphantom{1} yes\\
\hline
litter & all non-living biomass with a size greater than the limit for soil organic matter  and less than the minimum diameter chosen for dead wood, lying dead, in various states of decomposition above or within the mineral or organic soil & max diameter (= max diameter for deadwood) & 10 cm default, but may be chosen by country\\
\hline
 &  & layers included & includes entire O horizon\\
\hline
 &  & include belowground? & yes\\
\hline
soil organic matter & organic carbon in mineral soils to a specified depth & sampling depth & 30 cm default, but may be chosen by country\\
\hline
\end{tabu}
\end{table}

@@

Aboveground biomass, which is typically \textless200 t C
ha\textsuperscript{-1} but can exceed 700 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by the IPCC as ``all
biomass of living vegetation above the soil including stems, stumps,
branches, bark, seeds, and foliage'' \citep{ipcc_2006_2006}. IPCC's
guidance is that the understory may be excluded the understory if it
constitutes a ``minor'' component, \emph{where quantitative definitions
of ``understory'' and ``minor'' are not provided}, but where a commonly
applied minimum size sampling threshold for mature forests would be 10
cm stem diameter at breast height (DBH). A recent study characterizing
the contributions of trees in different DBH classes to ecosystem C
stocks and fluxes found that trees 1 - 10 cm DBH contributed up to
\textasciitilde8\% aboveground biomass, \textasciitilde17\% aboveground
woody net primary productivity (\(ANPP_{woody.stem}\)), and
\textasciitilde20\% woody mortality (\(M_{woody}\)) of mature
closed-canopy forests worldwide \citep{piponiot_distribution_2022}. In
regrowth forests, woodlands, or savannas, small trees and shrubs
contribute a much larger proportion of C stocks and fluxes
\citep{piponiot_distribution_2022, refs}, and, correspondingly, biomass
estimates for these ecosystems tend include smaller size classes
\citep[e.g.,][]{refs}. Beyond the minimum DBH sampled, forest censuses
and biomass estimates also differ in their inclusion of life forms other
than dicot trees -- including lianas, ferns, palms, and bamboo -- which
in some places can reach large sizes and/or constitute a large fraction
of forest C. \emph{{[}explain IPCC guidance{]}} Further, it is important
to note that this excludes standing dead wood, which is included in
remote sensing biomass estimates \citep{duncanson_aboveground_2021}.

@@

Belowground biomass is defined as ``all biomass of live roots''
\citep{ipcc_2006_2006}, a definition including both coarse roots, whose
biomass is typically estimated based on stem censuses and allometries or
belowground to aboveground biomass ratios, and fine roots, whose biomass
is typically estimated via extraction of roots from soil samples. The
former, which is typically \textless40 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is methodologically linked to
aboveground biomass estimates, sharing the same methodological sources
of variation, but tending to be far more uncertain. Fine root biomass
generally constitutes a much smaller C pool \citep[typically \textless5
t C ha\textsuperscript{-1},][]{anderson-teixeira_carbon_2021}, and IPCC
guidance is that it can be excluded when fine roots cannot be
distinguished empirically from soil organic matter or litter
\citep{ipcc_2006_2006}, which can be a painstaking process. Field
methods for estimating root biomass are highly variable. IPCC's default
method for Tier 1 estimates is to apply a ratio of belowground to
aboveground biomass, with default factors defined based on ecological
zone, continent, and forest age \citep{ipcc_2006_2006, ipcc_2019_2019}.

@@

Dead wood, which is typically \textless50 t C ha\textsuperscript{-1} but
can exceed 150 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by IPCC as ``all
non-living woody biomass not contained in the litter, either standing,
lying on the ground, or in the soil'' \citep{ipcc_2006_2006}. This pool
includes standing and fallen dead wood, stumps, and dead roots of
diameter ≥10 cm (or a diameter specified by the country). While dead
wood stocks and fluxes can be quite variable across forests
\citep{anderson-teixeira_carbon_2021}, and can at times be the dominant
pool in a forest ecosystem {[}e.g., following a severe natural
disturbance; \citet{carmona_coarse_2002}{]}, aboveground dead wood
remains relatively poorly characterized at a global scale
\citep{anderson-teixeira_carbon_2021}, and belowground dead wood is
rarely studied \citep{merganicova_dadwood_2012}. In turn, they are
poorly characterized in large-scale forest C budgets
\citep{pan_large_2011, harris_global_2021}, and IPCC's latest Tier 1
default values are based on just 1-31 references per climate zone
\citep[Table 2.2 in][]{ipcc_2019_2019}.

Litter is defined as including " all non-living biomass with a diameter
less than a minimum diameter chosen by the country (for example 10 cm),
lying dead, in various states of decomposition above the mineral or
organic soil. This includes litter (OL), fumic (OF), and humic (OH)
layers. Live fine roots (of less than the suggested diameter limit for
belowground biomass) are included in litter where they cannot be
distinguished from it empirically." (2003 IPCc GPG for LULUCF
(https://www.ipcc-nggip.iges.or.jp/public/gpglulucf/gpglulucf\_files/Glossary\_Acronyms\_BasicInfo/Glossary.pdf)
IPCC's latest Tier 1 default values are based on just 1-7 references per
climate zone \citep[Table 2.2 in][]{ipcc_2019_2019}.

@@

Soil organic matter is defined as ``Includes organic carbon in mineral
and organic soils (including peat) to a specified depth chosen by the
country and applied consistently through the time series. Live fine
roots (of less than the suggested diameter limit for belowground
biomass) are included with soil organic matter where they cannot be
distinguished from it empirically.''(2003 IPCc GPG for LULUCF
(https://www.ipcc-nggip.iges.or.jp/public/gpglulucf/gpglulucf\_files/Glossary\_Acronyms\_BasicInfo/Glossary.pdf)

@@

As of April 14, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

@@

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }\\
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB}\\
\hline
\textbf{Biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass &  &  &  & \\
\hline
delta.biomass &  &  &  & \\
\hline
NPP\_woody &  &  &  & \\
\hline
\textbf{Aboveground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_ag &  &  &  & \\
\hline
biomass\_ag\_woody &  &  &  & \\
\hline
biomass\_ag\_foliage &  &  &  & \\
\hline
delta.agb &  &  &  & \\
\hline
ANPP\_woody\_stem &  &  &  & \\
\hline
ANPP\_foliage &  &  &  & \\
\hline
woody\_mortality &  &  &  & \\
\hline
\textbf{Belowground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_root &  &  &  & \\
\hline
biomass\_root\_fine &  &  &  & \\
\hline
biomass\_root\_coarse &  &  &  & \\
\hline
delta.biomass\_root &  &  &  & \\
\hline
BNPP\_root &  &  &  & \\
\hline
BNPP\_root\_fine &  &  &  & \\
\hline
BNPP\_root\_coarse &  &  &  & \\
\hline
\textbf{Dead wood} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
deadwood &  &  &  & \\
\hline
deadwood\_standing &  &  &  & \\
\hline
deadwood\_down &  &  &  & \\
\hline
delta.deadwood &  &  &  & \\
\hline
delta.deadwood\_standing &  &  &  & \\
\hline
delta.deadwood\_down &  &  &  & \\
\hline
\textbf{Litter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
O.horizon &  &  &  & \\
\hline
delta.O.horizon &  &  &  & \\
\hline
NPP\_litterfall &  &  &  & \\
\hline
R\_het\_litter &  &  &  & \\
\hline
\textbf{Soil organic matter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
SOM / SOC &  &  &  & \\
\hline
delta.SOM / delta.SOC &  &  &  & \\
\hline
R\_het\_soil &  &  &  & \\
\hline
\textbf{TOTAL} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
\end{longtabu}

@@

As of April 14, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}

>>>>

The International Panel on Climate Change (IPCC) provides guidance for
national greenhouse gas inventories for reporting to the United Nations
Framework Convention on Climate Change
\citep[UNFCCC,][]{ipcc_2006_2006, ipcc_2019_2019}. Under this guidance,
greenhouse gas inventories include all managed land, including most of
the world's forest land \citep{ogle_delineating_2018}. The IPCC
inventory guidelines include specific instructions for accounting for
greenhouse gas (mainly CO\textsubscript{2}) exchanges between forest
land and the atmosphere \citep{ipcc_agriculture_2006, ipcc_2019_2019}.
This guidance has improved over the years as more of the relevant
underlying data has become available
\citep{requenasuarez_estimating_2019, rozendaal_aboveground_2022}, but
there remains room for continuous improvement as the science advances.
For example, the year following the release of the latest IPCC
guidelines, \citet{cook-patton_mapping_2020} found that the latest
default rates may underestimate rates of C accumulation in regrowth
forests by 32\% on average and fail to capture eight-fold variation
within ecozones. In addition, \citet{cuni-sanchez_high_2021} found that
aboveground C stocks in mature African tropical montane forests were
two-thirds higher than the IPCC default values for these forests. This
rapid evolution of scientific information on the climate mitigation
potential of forests is beneficial to climate mitigation efforts, but
requires improved mechanisms for communicating the latest information
from scientific researchers to the practitioners who need reliable
estimates for greenhouse gas mitigation planning. Moreover, high
variability of forest C cycling within ecozones
\citep[e.g.,][]{cook-patton_mapping_2020, cuni-sanchez_high_2021}
implies that it is useful for practitioners to have access to
locally-specific information, when available.

@@

\caption{\label{tab:table_pools}\textbf{IPCC-defined forest carbon pools with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{pool} & \textbf{definition} & \textbf{important sources of estimate variation} & \textbf{IPCC guidance}\\
\hline
aboveground biomass & all biomass of living vegetation & min dbh & may exclude understory if minor component\\
\hline
 &  & include non-dicot trees? & ?\\
\hline
 &  & include dead standing? & no\\
\hline
 &  & biomass allometry & ?\\
\hline
belowground biomass & all biomass of live roots & all factors relevant to aboveground biomass & see above\\
\hline
 &  & allometry or assumed ratio of below- to above-ground biomass (R) & can estimate based on R\\
\hline
 &  & min root diameter & may exclude fine roots\\
\hline
 &  & sampling depth & ?\\
\hline
dead wood & all non-living woody biomass above a specified diameter, aboveground or belowground & min diameter & 10 cm default, but may be chosen by country\\
\hline
 &  & include belowground? & \vphantom{1} yes\\
\hline
litter & all non-living biomass, within specified size limits, in various states of decomposition above or within the mineral or organic soil & max diameter (= min diameter for deadwood) & 10 cm default, but may be chosen by country\\
\hline
 &  & min size (= size limit for soil organic matter) & ?\\
\hline
 &  & layers included & entire O horizon: litter (OL),  fumic (OF),  and  humic (OH) layers\\
\hline
 &  & include belowground? & yes\\
\hline
soil organic matter & organic carbon in mineral soils to a specified depth & sampling depth & 30 cm default, but may be chosen by country\\
\hline
\end{tabu}
\end{table}

@@

Aboveground biomass, which is typically \textless200 t C
ha\textsuperscript{-1} but can exceed 700 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by the IPCC as ``all
biomass of living vegetation above the soil including stems, stumps,
branches, bark, seeds, and foliage''
\citep{ipcc_good_2003, ipcc_2006_2006}. IPCC's guidance is that the
understory may be excluded the understory if it constitutes a ``minor''
component, \emph{where quantitative definitions of ``understory'' and
``minor'' are not provided}, but where a commonly applied minimum size
sampling threshold for mature forests would be 10 cm stem diameter at
breast height (DBH). A recent study characterizing the contributions of
trees in different DBH classes to ecosystem C stocks and fluxes found
that trees 1 - 10 cm DBH contributed up to \textasciitilde8\%
aboveground biomass, \textasciitilde17\% aboveground woody net primary
productivity (\(ANPP_{woody.stem}\)), and \textasciitilde20\% woody
mortality (\(M_{woody}\)) of mature closed-canopy forests worldwide
\citep{piponiot_distribution_2022}. In regrowth forests, woodlands, or
savannas, small trees and shrubs contribute a much larger proportion of
C stocks and fluxes \citep{piponiot_distribution_2022, refs}, and,
correspondingly, biomass estimates for these ecosystems tend include
smaller size classes \citep[e.g.,][]{refs}. Beyond the minimum DBH
sampled, forest censuses and biomass estimates also differ in their
inclusion of life forms other than dicot trees -- including lianas,
ferns, palms, and bamboo -- which in some places can reach large sizes
and/or constitute a large fraction of forest C. \emph{{[}explain IPCC
guidance{]}} Further, it is important to note that this excludes
standing dead wood, which is included in remote sensing biomass
estimates \citep{duncanson_aboveground_2021}.

@@

Belowground biomass is defined as ``all biomass of live roots''
\citep{ipcc_good_2003, ipcc_2006_2006}, a definition including both
coarse roots, whose biomass is typically estimated based on stem
censuses and allometries or belowground to aboveground biomass ratios,
and fine roots, whose biomass is typically estimated via extraction of
roots from soil samples. The former, which is typically \textless40 t C
ha\textsuperscript{-1} \citep{anderson-teixeira_carbon_2021}, is
methodologically linked to aboveground biomass estimates, sharing the
same methodological sources of variation, but tending to be far more
uncertain. Fine root biomass generally constitutes a much smaller C pool
\citep[typically \textless5 t C
ha\textsuperscript{-1},][]{anderson-teixeira_carbon_2021}, and IPCC
guidance is that it can be excluded when fine roots cannot be
distinguished empirically from soil organic matter or litter
\citep{ipcc_2006_2006}, which can be a painstaking process. Field
methods for estimating root biomass are highly variable. IPCC's default
method for Tier 1 estimates is to apply a ratio of belowground to
aboveground biomass, with default factors defined based on ecological
zone, continent, and forest age \citep{ipcc_2006_2006, ipcc_2019_2019}.

@@

Dead wood, which is typically \textless50 t C ha\textsuperscript{-1} but
can exceed 150 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by IPCC as ``all
non-living woody biomass not contained in the litter, either standing,
lying on the ground, or in the soil''
\citep{ipcc_good_2003, ipcc_2006_2006}. This pool includes standing and
fallen dead wood, stumps, and dead roots of diameter ≥10 cm (or a
diameter specified by the country). While dead wood stocks and fluxes
can be quite variable across forests
\citep{anderson-teixeira_carbon_2021}, and can at times be the dominant
pool in a forest ecosystem {[}e.g., following a severe natural
disturbance; \citet{carmona_coarse_2002}{]}, aboveground dead wood
remains relatively poorly characterized at a global scale
\citep{anderson-teixeira_carbon_2021}, and belowground dead wood is
rarely studied \citep{merganicova_dadwood_2012}. In turn, they are
poorly characterized in large-scale forest C budgets
\citep{pan_large_2011, harris_global_2021}, and IPCC's latest Tier 1
default values are based on just 1-31 references per climate zone
\citep[Table 2.2 in][]{ipcc_2019_2019}.

Litter, which is typically \textless40 t C ha\textsuperscript{-1} but
can exceed 100 t C ha\textsuperscript{-1}
\citep{anderson-teixeira_carbon_2021}, is defined by IPCCC as including
``all non-living biomass with a diameter less than a minimum diameter
chosen by the country (for example 10 cm), lying dead, in various states
of decomposition above the mineral or organic soil''
\citep{ipcc_good_2003, ipcc_2006_2006}. As noted above, live fine roots
may be included in litter when difficult to separate empirically. The
definition includes the entire O horizion, including litter (OL), fumic
(OF), and humic (OH) layers, in addition to litter embedded within the
soil. This definition contrasts with empirical studies that focus on
aboveground litter, often including only the OL layer in the definition
of litter, and do not always specify the components included. Similar to
dead wood, litter is poorly characterized in large-scale forest C
budgets \citep{pan_large_2011, harris_global_2021}, and IPCC's latest
Tier 1 default values are based on just 1-7 references per climate zone
\citep[Table 2.2 in][]{ipcc_2019_2019}.

@@

Soil organic matter is defined as ``Includes organic carbon in mineral
and organic soils (including peat) to a specified depth chosen by the
country and applied consistently through the time series. Live fine
roots (of less than the suggested diameter limit for belowground
biomass) are included with soil organic matter where they cannot be
distinguished from it empirically.''
\citep{ipcc_good_2003, ipcc_2006_2006}.

@@

As of April 15, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

@@

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:table_variables}\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. }\\
\hline
\textbf{variable} & \textbf{n in ForC} & \textbf{n independent records in ForC} & \textbf{n reviewed} & \textbf{n sent to EFDB}\\
\hline
\textbf{Biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass &  &  &  & \\
\hline
delta.biomass &  &  &  & \\
\hline
NPP\_woody &  &  &  & \\
\hline
\textbf{Aboveground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_ag &  &  &  & \\
\hline
biomass\_ag\_woody &  &  &  & \\
\hline
biomass\_ag\_foliage &  &  &  & \\
\hline
delta.agb &  &  &  & \\
\hline
ANPP\_woody\_stem &  &  &  & \\
\hline
ANPP\_foliage &  &  &  & \\
\hline
woody\_mortality &  &  &  & \\
\hline
\textbf{Belowground biomass} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
biomass\_root &  &  &  & \\
\hline
biomass\_root\_fine &  &  &  & \\
\hline
biomass\_root\_coarse &  &  &  & \\
\hline
delta.biomass\_root &  &  &  & \\
\hline
BNPP\_root &  &  &  & \\
\hline
BNPP\_root\_fine &  &  &  & \\
\hline
BNPP\_root\_coarse &  &  &  & \\
\hline
\textbf{Dead wood} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
deadwood &  &  &  & \\
\hline
deadwood\_standing &  &  &  & \\
\hline
deadwood\_down &  &  &  & \\
\hline
delta.deadwood &  &  &  & \\
\hline
delta.deadwood\_standing &  &  &  & \\
\hline
delta.deadwood\_down &  &  &  & \\
\hline
\textbf{Litter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
O.horizon &  &  &  & \\
\hline
delta.O.horizon &  &  &  & \\
\hline
litter &  &  &  & \\
\hline
delta.litter &  &  &  & \\
\hline
NPP\_litterfall &  &  &  & \\
\hline
R\_het\_litter &  &  &  & \\
\hline
\textbf{Soil organic matter} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
SOM / SOC &  &  &  & \\
\hline
delta.SOM / delta.SOC &  &  &  & \\
\hline
R\_het\_soil &  &  &  & \\
\hline
\textbf{TOTAL} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hline
\end{longtabu}

@@

As of April 15, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}
